|

### 2021-02-09 appendix/appendix.Rmd
add het effects exp02, description exp03

\footnotesize
```{r loading, warning=F, message=F, error=F, cache=T}
# Install and load required packages
packages <- c("cjoint", "cregg", "estimatr", "grf", "kableExtra", "janitor",
              "quanteda", "seededlda", "stargazer", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

@@

We also note that there is another word cluster on the left. It contains words
that indicate that some respondents do not support lynchings, such as _não_
(no), _opção_ (choice), _nada_ (nothing), _justifica_ (justifies),
_justificável_ (justifiable), and _escolher_ (choose).

@@

Lastly, we estimate a latent Dirichlet allocation (LDA) model to identify the
three most important topics in our corpus. The first topic includes words that
describes lynching perpetrators, as it contains the words like _polícia_
(police), _pessoas_ (people), and _família_ (family). The second topic
identifies the same words we associate with respondents who are against
lynchings, such as _nenhum_ (none), _opção_ (choice), _não_ (no), and _contra_
(against). The last topic, in contrast, refer to victim and crime
characteristics, which have also appeared in our previous estimations. Some of
the most common words in this group are _crime_ (crime), _criança_ (child),
_estupro_ (rape), _vítima_ (victim), _porque_ (because), _idoso_ (elderly),
_grave_ (serious), and _molestar_ (molest).

@@

m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
m2 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02)
m3 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
m4 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)

stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
          p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp02main",
          title = "Experiment 02 -- Main Results", style = "apsr",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Police does not patrol area", "Justice too slow",
                               "Punishment not harsh enough", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")
```
\normalsize

## Demographic Characteristics and Lynching Support

Here we evaluate the impact of individual characteristics on lynching support.
We combine all treatment and control groups and measure whether demographic
information, which we collected in our questionnaire, changes baseline levels.

\footnotesize
```{r exp02-demographics, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp02_group <- df_exp02 %>%
  filter(gender %in% c("Female", "Male"),
         race %in% c("Asian", "Black", "Mixed Race", "White", "Indigenous"),
         education %in% c("College", "Graduate School", "Primary School",
                          "Secondary School", "High School")) %>%
  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
                            "Indigenous")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ as.character(education)),
         education2 = fct_relevel(education2, "Primary or Secondary School",
                                  "High School", "College", "Graduate School")) %>%
  mutate(views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad")) %>%
  mutate(views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad")) %>%
  mutate(ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
                                "Center-Right", "Right", "Don't Know",
                                "Rather Not Say")) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_),
  household_income2 = fct_relevel(household_income2, "Up to R$3,000", "From R$3,001 to R$5,000",
                                  "Above R$5,000"))

# Models
m1 <- lm(exp02_outcomes ~ gender, data = df_exp02_group)
m2 <- lm(exp02_outcomes ~ age, data = df_exp02_group)
m3 <- lm(exp02_outcomes ~ race, data = df_exp02_group)
m4 <- lm(exp02_outcomes ~ education2, data = df_exp02_group)
m5 <- lm(exp02_outcomes ~ household_income2, data = df_exp02_group)
m6 <- lm(exp02_outcomes ~ ideology, data = df_exp02_group)
m7 <- lm(exp02_outcomes ~ previous_victim_dummy, data = df_exp02_group)
m8 <- lm(exp02_outcomes ~ views_police, data = df_exp02_group)
m9 <- lm(exp02_outcomes ~ views_justice, data = df_exp02_group)

# Tables (robust standard errors from estimatr)
stargazer(m1, m2, m3, m4, m5, se = starprep(m1, m2, m3, m4, m5),
          p = starprep(m1, m2, m3, m4, m5, se_type = "HC1", stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp02demo1",
          title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}", style = "apsr",
          column.labels = c("Gender", "Age", "Race", "Education", "Income"),
          covariate.labels = c("Male", "Years", "Black", "Mixed Race",
                               "Asian", "Indigenous", "High School", "College",
                               "Graduate School", "3,001 to 5,000 BRL", "5,000+ BRL"),
          column.sep.width = "2pt", notes = c("Reference categories: Model 1: Female;
                                              Model 3: White; Model 4: Primary or secondary school;",
                                              "Model 5: Up to 3,000 BRL. Robust standard errors in
                                              parentheses."),
          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")

```
\clearpage

```{r exp02-demographics2, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
stargazer(m6, m7, m8, m9, se = starprep(m6, m7, m8, m9),
          p = starprep(m6, m7, m8, m9, se_type = "HC2", stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp02demo2",
          title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}", style = "apsr",
          column.labels = c("Ideology", "Previous Victimization", "Police",
                            "Judiciary"),
          covariate.labels = c("Left", "Center-Left", "Center-Right", "Right",
                               "Don't Know", "Rather Not Say", "Yes",
                               "Very Good", "Good", "Bad", "Very Bad",
                               "Don't Know", "Rather Not Say",
                               "Very Good", "Good", "Bad", "Very Bad",
                               "Don't Know", "Rather Not Say"),
          column.sep.width = "2pt", notes = c("Reference categories: Model 1: Center;
                                              Model 2: No; Model 3: Regular; Model 4: Regular.",
                                              "Robust standard errors in parentheses."),
          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")
```
\normalsize

\footnotesize
```{r exp02-forest, warning=F, error=F, message=F, cache=T, fig.width=7, fig.height=6, eval=F}
df_exp02_police <- df_exp02_group %>%
  select(exp02_outcomes, exp02_police_treat, gender, age, race, education, household_income2, ideology, views_police, views_justice) %>%
  mutate(exp02_police_treat = as.numeric(exp02_police_treat))

  drop_na()

library(FindIt)
F1 <-FindIt(model.treat = exp02_outcomes ~ exp02_police_treat,
            model.main = ~ race,
            model.int = ~ race,
            data = df_exp02_police,
            type = "binary",
            treat.type = "single")

F1 <-FindIt(model.treat= outcome ~ treat,
            model.main= ~ age+educ+black+hisp+white+marr+nodegr+log.re75+u75,
            model.int= ~ age+educ+black+hisp+white+marr+nodegr+log.re75+u75, data = LaLonde, type="binary", treat.type="single")

cases <- sample(seq_len(nrow(df_exp02_police)), round(nrow(df_exp02_police) * .6))
train <- df_exp02_police[cases, ]
test <- df_exp02_police[-cases, ]

x <- c("age")
g <- c("gender", "race", "education", "household_income2",
"ideology", "views_police", "views_justice")
X2 <- model.matrix(~ 0 + ., train[c(x, g)])

cf <- causal_forest(
  X = X2,
  Y = as.numeric(train$exp02_outcomes),
  W = as.integer(train$exp02_police_treat),
  num.trees = 1000,
  seed = 1839
)

cf %>%
  variable_importance() %>%
  as.data.frame() %>%
  mutate(variable = colnames(cf$X.orig)) %>%
  arrange(desc(V1))

preds <- predict(
  object = cf,
  newdata = model.matrix(~ ., data = test[, 3:ncol(train)]),
  estimate.variance = TRUE
)

test$preds <- preds$predictions

ggplot(test, aes(x = views_justice, y = preds)) +
  geom_point() +
  geom_smooth(method = "loess", span = 1) +
  theme_light()

average_treatment_effect(cf, target.sample = "all")
tree <- get_tree(cf, 1)
plot(tree)

dr_scores <- double_robust_scores(cf)
tree <- policy_tree(X2, dr_scores, 3)
plot(tree)
plot_htes(preds, ci = TRUE)
```

@@

>>>>

\footnotesize
```{r loading, warning=F, message=F, error=F, cache=T}
# Install and load required packages
packages <- c("bartCause", "cjoint", "cregg", "estimatr", "kableExtra",
              "janitor", "quanteda", "seededlda", "stargazer", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

@@

We note that there is another word cluster on the left. It contains words
that indicate that some respondents do not support lynchings, such as _não_
(no), _opção_ (choice), _nada_ (nothing), _justifica_ (justifies),
_justificável_ (justifiable), and _escolher_ (choose).

@@

We estimate a latent Dirichlet allocation (LDA) model to identify the
three most important topics in our corpus. The first topic includes words that
describes lynching perpetrators, as it contains the words like _polícia_
(police), _pessoas_ (people), and _família_ (family). The second topic
identifies the same words we associate with respondents who are against
lynchings, such as _nenhum_ (none), _opção_ (choice), _não_ (no), and _contra_
(against). The last topic, in contrast, refer to victim and crime
characteristics, which have also appeared in our previous estimations. Some of
the most common words in this group are _crime_ (crime), _criança_ (child),
_estupro_ (rape), _vítima_ (victim), _porque_ (because), _idoso_ (elderly),
_grave_ (serious), and _molestar_ (molest).

@@

# Models
m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
m2 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02)
m3 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
m4 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)

# Table
stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
          p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp02main",
          title = "Experiment 02 -- Main Results", style = "apsr",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Police does not patrol area", "Justice too slow",
                               "Punishment not harsh enough", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

@@

## Heterogeneous Effects

We estimate heterogeneous effects for our experiment using Bayesian Additive
Regression Trees (BART) [@chipman2010bart; @hill2011bayesian]. BART methods
allow users to detect non-linear interactions and are insensitive to the choice
of tuning parameters, so they are well-suited to analyze observational and
experimental data [@green2012modeling]. More specifically, we employ the
`bartCause` package, which is designed to estimate causal inference models.

### Treatment 01: Police Ineffectiveness

Our results indicate that the effects for this treatment arm is null in every
model specification. We find no evidence of heterogeneous effects.

\footnotesize
```{r exp02-bart01, warning=F, error=F, message=F, cache=T}
df_exp02_het <- df_exp02 %>%
  filter(gender %in% c("Female", "Male")) %>%
  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
                            "Indigenous"),
         education = fct_relevel(education, "Primary School", "Secondary School",
                                  "High School", "College", "Graduate School"),
         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad"),
         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
                                     "Bad", "Very Bad"),
         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
                                         "Above R$20,000"),
         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
         death_penalty = fct_relevel(death_penalty, "Yes", "No"))

df_exp02_police <- df_exp02_het %>%
  mutate(exp02_police_treat = as.numeric(exp02_police_treat)) %>%
  drop_na(exp02_police_treat)

# Gender
summary(bartc(exp02_outcomes, exp02_police_treat, gender,
              group.by = gender, group.effects = TRUE, data = df_exp02_police,
              n.chains = 5L, seed = 144))

# Race
summary(bartc(exp02_outcomes, exp02_police_treat, race,
              group.by = race, group.effects = TRUE, data = df_exp02_police,
              n.chains = 5L, seed = 144))

# Education
summary(bartc(exp02_outcomes, exp02_police_treat, education,
              group.by = education, group.effects = TRUE, data = df_exp02_police,
              n.chains = 5L, seed = 144))

# Household Income
summary(bartc(exp02_outcomes, exp02_police_treat, household_income,
              group.by = household_income, group.effects = TRUE, data = df_exp02_police,
              n.chains = 5L, seed = 144))

# Political Ideology
summary(bartc(exp02_outcomes, exp02_police_treat, ideology,
              group.by = ideology, group.effects = TRUE, data = df_exp02_police,
              n.chains = 5L, seed = 144))

# Support for Death Penalty
summary(bartc(exp02_outcomes, exp02_police_treat, death_penalty,
              group.by = death_penalty, group.effects = TRUE, data = df_exp02_police,
              n.chains = 5L, seed = 144))

# Opinion on the Police
summary(bartc(exp02_outcomes, exp02_police_treat, views_police,
              group.by = views_police, group.effects = TRUE, data = df_exp02_police,
              n.chains = 5L, seed = 144))

# Opinion on the Judicial System
summary(bartc(exp02_outcomes, exp02_police_treat, views_justice,
              group.by = views_police, group.effects = TRUE, data = df_exp02_police,
              n.chains = 5L, seed = 144))
```
\normalsize

### Treatment 02: Criminal Justice Ineffectiveness

We do not find any evidence of heterogeneous treatment effects in this
condition either.

\footnotesize
```{r exp02-bart02, warning=F, error=F, message=F, cache=T}
df_exp02_slow_justice <- df_exp02_het %>%
  mutate(exp02_slow_justice_treat = as.numeric(exp02_slow_justice_treat)) %>%
  drop_na(exp02_slow_justice_treat)

# Gender
summary(bartc(exp02_outcomes, exp02_slow_justice_treat, gender,
              group.by = gender, group.effects = TRUE, data = df_exp02_slow_justice,
              n.chains = 5L, seed = 144))

# Race
# summary(bartc(exp02_outcomes, exp02_slow_justice_treat, race,
              # group.by = race, group.effects = TRUE, data = df_exp02_slow_justice,
              # n.chains = 5L, seed = 144))

# Education
summary(bartc(exp02_outcomes, exp02_slow_justice_treat, education,
              group.by = education, group.effects = TRUE, data = df_exp02_slow_justice,
              n.chains = 5L, seed = 144))

# Household Income
summary(bartc(exp02_outcomes, exp02_slow_justice_treat, household_income,
              group.by = household_income, group.effects = TRUE, data = df_exp02_slow_justice,
              n.chains = 5L, seed = 144))

# Political Ideology
summary(bartc(exp02_outcomes, exp02_slow_justice_treat, ideology,
              group.by = ideology, group.effects = TRUE, data = df_exp02_slow_justice,
              n.chains = 5L, seed = 144))

# Support for Death Penalty
summary(bartc(exp02_outcomes, exp02_slow_justice_treat, death_penalty,
              group.by = death_penalty, group.effects = TRUE, data = df_exp02_slow_justice,
              n.chains = 5L, seed = 144))

# Opinion on the Police
summary(bartc(exp02_outcomes, exp02_slow_justice_treat, views_police,
              group.by = views_police, group.effects = TRUE, data = df_exp02_slow_justice,
              n.chains = 5L, seed = 144))

# Opinion on the Judicial System
summary(bartc(exp02_outcomes, exp02_slow_justice_treat, views_justice,
              group.by = views_police, group.effects = TRUE, data = df_exp02_slow_justice,
              n.chains = 5L, seed = 144))
```
\normalsize

### Treatment 03: Demand for Harsher Legal Punishment

As in the last two series of models, our results show no evidence of
heterogeneous treatment effects.

\footnotesize
```{r exp02-bart03, warning=F, error=F, message=F, cache=T}
df_exp02_small_punishment <- df_exp02_het %>%
  mutate(exp02_small_punishment_treat = as.numeric(exp02_small_punishment_treat)) %>%
  drop_na(exp02_small_punishment_treat)

# Gender
summary(bartc(exp02_outcomes, exp02_small_punishment_treat, gender,
              group.by = gender, group.effects = TRUE, data = df_exp02_small_punishment,
              n.chains = 5L, seed = 144))

# Race
summary(bartc(exp02_outcomes, exp02_small_punishment_treat, race,
              group.by = race, group.effects = TRUE, data = df_exp02_small_punishment,
              n.chains = 5L, seed = 144))

# Education
summary(bartc(exp02_outcomes, exp02_small_punishment_treat, education,
              group.by = education, group.effects = TRUE, data = df_exp02_small_punishment,
              n.chains = 5L, seed = 144))

# Household Income
summary(bartc(exp02_outcomes, exp02_small_punishment_treat, household_income2,
              group.by = household_income2, group.effects = TRUE, data = df_exp02_small_punishment,
              n.chains = 5L, seed = 144))

# Political Ideology
summary(bartc(exp02_outcomes, exp02_small_punishment_treat, ideology,
              group.by = ideology, group.effects = TRUE, data = df_exp02_small_punishment,
              n.chains = 5L, seed = 144))

# Support for Death Penalty
summary(bartc(exp02_outcomes, exp02_small_punishment_treat, death_penalty,
              group.by = death_penalty, group.effects = TRUE, data = df_exp02_small_punishment,
              n.chains = 5L, seed = 144))

# Opinion on the Police
summary(bartc(exp02_outcomes, exp02_small_punishment_treat, views_police,
              group.by = views_police, group.effects = TRUE, data = df_exp02_small_punishment,
              n.chains = 5L, seed = 144))

# Opinion on the Judicial System
summary(bartc(exp02_outcomes, exp02_small_punishment_treat, views_justice,
              group.by = views_police, group.effects = TRUE, data = df_exp02_small_punishment,
              n.chains = 5L, seed = 144))
```
\normalsize

# Experiment 03

Our last experiment measures the effect of information provision on attitudes
about lynching. In particular, we test whether reminding respondents
about the legal and social consequences of vigilante justice reduces the
subjects' level of support for such practice.

The experiment has three treatment conditions and a control group. In all of
them we present respondents with a short statement affirming that some
Brazilians support vigilantism under certain conditions. Respondents were asked
to use 0 to 49 if they disagree, 50 if they neither agree nor disagree, and
50-100 if they agree with the sentence.

Each of the three treatment groups received a different message about the
legal or social consequences of lynching in Brazil. In the first treatment
arm, we informed subjects about how the Brazilian constitution and penal code
punishes civilian violence. The second treatment group was notified about
the human rights guarantees enshrined in Brazil's legal framework. The last
group read a vignette that mentions how lynchings can spark _vendettas_ and
initiate a cycle of violence in the community. Subjects in the control group
received no information about the consequences of lynchings. The text shown
to the control and treatment groups can be read below.

* *Control group*: In Brazil, some people believe that lynching may be
  justified under certain conditions. To what degree do you agree or disagree
  that lynching can be justified? Please use the slider below to indicate your
  preference. For disagreement, use 0 to 49; for agreement, use 51 to 100.
  Please use 50 if you neither agree nor disagree.[^control-exp03]

[^control-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
linchamentos são justificados sob certas condições. O quanto você concorda ou
discorda que linchamentos podem ser justificados? Por favor, use a barra abaixo
para indicar sua preferência. Para indicar que discorda, use de 0 a 49; para
concordar, use de 51 a 100. Por favor, use 50 caso você não concorde nem
discorde.

* *Treatment 01 - Legal punishment for lynching perpetrators*: In Brazil,
  some people believe that lynching may be justified under certain conditions.
  **However, the Brazilian constitution and penal code strictly forbid
  lynching and those involved can be accused of torture or murder**. To what
  degree do you agree or disagree that lynching can be justified? Please use
  the slider below to indicate your preference. For disagreement, use 0 to 49;
  for agreement, use 51 to 100. Please use 50 if you neither agree nor
  disagree.[^treat01-exp03]

[^treat01-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
linchamentos são justificados sob certas condições. **Entretanto, a
constituição e o código penal do Brasil proíbem estritamente os linchamentos e
os envolvidos podem ser acusados de tortura ou assassinato.** O quanto você
concorda ou discorda que linchamentos podem ser justificados? Por favor, use a
barra abaixo para indicar sua preferência. Para indicar que discorda, use de 0
a 49; para concordar, use de 51 a 100. Por favor, use 50 caso você não concorde
nem discorde.

* *Treatment 02 - Human rights*: In Brazil, some people believe that lynching
  may be justified under certain conditions. **However, the Brazilian
  constitution states that all individuals have the right of not being
  tortured, including criminals**. To what degree do you agree or disagree that
  lynching can be justified? Please use the slider below to indicate your
  preference. For disagreement, use 0 to 49; for agreement, use 51 to 100.
  Please use 50 if you neither agree nor disagree.[^treat02-exp03]

[^treat02-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
linchamentos são justificados sob certas condições. **Entretanto, a
constituição do Brasil afirma que todos os indivíduos têm o direito de não
serem torturados, inclusive criminosos**. O quanto você concorda ou discorda que
linchamentos podem ser justificados? Por favor, use a barra abaixo para indicar
sua preferência. Para indicar que discorda, use de 0 a 49; para concordar, use
de 51 a 100. Por favor, use 50 caso você não concorde nem discorde.

* *Treatment 03 - Vendettas*: In Brazil, some people believe that lynching
  may be justified under certain conditions. **However, lynchings can trigger
  a new cycle of violence as the family or friends of the victim may retaliate
  the community**. To what degree do you agree or disagree that lynching can be
  justified? Please use the slider below to indicate your preference. For
  disagreement, use 0 to 49; for agreement, use 51 to 100. Please use 50 if you
  neither agree nor disagree.[^treat03-exp03]

[^treat03-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
linchamentos são justificados sob certas condições. **Entretanto, linchamentos
podem iniciar um ciclo de violência pois a família ou amigos da vítima podem
retaliar a comunidade**. O quanto você concorda ou discorda que linchamentos
podem ser justificados? Por favor, use a barra abaixo para indicar sua
preferência. Para indicar que discorda, use de 0 a 49; para concordar, use de
51 a 100. Por favor, use 50 caso você não concorde nem discorde.

Our results are available in table XXX below.
